### 2018-09-15 Sections/conclusion_the_vision_of_the_quantum_internet.tex
Proof reading

We have presented an early formulation and analysis of quantum networking protocols with the vision of enabling a future quantum internet, where quantum resources can be shared and communicated in much the same way as is presently done with digital assets. Whilst it is hard to foresee exactly how future quantum networks will be implemented, many of the central ideas presented here will be applicable across architectures and implementations on an ad hoc basis.

@@

The quantum internet will allow quantum computation to become distributed, not just outsourced. In the same way that many present-day classical algorithms are heavily parallelised and distributed across large clusters, CUDA cores\index{CUDA}, or even across the internet itself (e.g the SETI project\index{SETI project}), quantum networks will allow the distribution of quantum computation across many nodes, either in parallel, in series, or in a modularised fashion. This will be pivotal to achieving scalability. Keeping in mind that the classical-equivalent power of a quantum computer may grow exponentially with the number of qubits, it is highly desirable to squeeze out every last available qubit for our computations -- every qubit is worth more than the last.

>>>>

We have presented an early formulation and analysis of quantum networking protocols with the vision of enabling a future quantum internet, where quantum resources can be shared and communicated in much the same way as is presently done with digital assets. Whilst it's hard to foresee exactly how future quantum networks will be implemented, many of the central ideas presented here will be applicable across architectures and implementations on an ad hoc basis.

@@

The quantum internet will allow quantum computation to become distributed, not just outsourced. In the same way that many present-day classical algorithms are heavily parallelised and distributed across large clusters, CUDA cores\index{CUDA}, or even across the internet itself (e.g the SETI project\index{SETI project}), quantum networks will allow the distribution of quantum computation across many nodes, either in parallel, in series, or in a modularised fashion. This will be pivotal to achieving scalability. Keeping in mind that the classical-equivalent power of a quantum computer may grow exponentially with the number of qubits, it is highly desirable to squeeze out every last available qubit for our computations -- every qubit is worth more than the last!

### 2018-09-15 Sections/essay_quantcoin.tex
Proof reading

\dropcap{T}{he} advent of cryptocurrencies\index{Cryptocurrencies} (Sec.~\ref{sec:bitcoin_blockchain}) places the death of fiat currency\index{Fiat currency} firmly on the horizon. Central banks around the world have been consistently inflating and devaluing national currencies, destroying their integrity through loose print-on-demand monetary policies to finance ever-increasing debt. National currencies and currency unions sit at the brink of crumbling. Can we opt out? Is there an alternative?

@@

For these reasons, gold\index{Gold standard} for thousands of years was almost universally accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies like BitCoin\index{Bitcoin} have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as the cryptocurrencies exhibit these desired traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

We propose that units of quantum computation meet these criteria very well. The only way to forge new computations is via investment into infrastructure, which has direct monetary cost and cannot be mitigated. Recent history has shown us that Moore's Law\index{Moore's Law} has made the growth in classical computing power highly predictable and relatively stable over time, and it is to be expected that a quantum Moore's Law will hold.

@@

Existing Blockchain-based cryptocurrencies like Bitcoin\index{Blockchain}\index{Bitcoin} (Sec.~\ref{sec:bitcoin_blockchain}) are actually examples of computation-backed currencies, where the mining process requires brute-force computation of a large number of SHA256\index{SHA256} hash functions\index{Hash functions}, to discover hashes satisfying certain constraints. Unfortunately, however, in the case of Bitcoin these computations are wasted, since they are not solving any problems of merit. Rather miners are made to perform them purely for the sake of imposing artificial scarcity via `proof-of-work'\index{Proof-of-work}\footnote{This proof-of-work notion was originally borrowed from the Hashcash\index{Hashcash} protocol for preventing email spamming.}.

QuantCoin\texttrademark\,\index{QuantCoin\texttrademark} (Sec.~\ref{sec:quant_coin_technical}) on the other hand backs the currency with real-world computations of value, as determined by market participants at the time, a far better utilisation of computational power, with far greater confidence in its objective monetary value. Such a currency is no longer backed purely by the psychology of scarcity\index{Scarcity}, but also the economic value of executing useful quantum algorithms on real-world data. Thanks to homomorphic encryption\index{Homomorphic encryption} and blind quantum computing\index{Blind quantum computation}, users' data may be protected from eavesdropping end-to-end, from when Alice sends her data to Bob to when she receives back the final result.

@@

Because future contracts have predetermined times until maturity, they also serve the very helpful role of being hedging\index{Hedging} instruments, an important tool for end-users of computation who may wish to lock in prices in advance to mitigate market risk.

@@

Consider the time-share future contract model as a basis for a currency. Unlike fiat currency, this monetary system would not be inflationary since the commodity backing the currency is one which cannot be easily counterfeited -- the only way to make more currency is to provide more genuine, functional, online qubits, which increases the money supply over time in tandem with the underlying asset backing it. This would in effect be a full-reserve banking system\index{Full-reserve banking}, where the direct one-to-one convertibility between currency (forward contracts on computation) and its backing asset (time-shared access to physical qubits) eliminates the money multiplier\index{Money multiplier}, a system essentially immune to bank runs\index{Bank runs}.

@@

In a strategically fractured world, where multiple, independent quantum internets may exist in isolation to one another, partitioned along geo-strategic boundaries, each with their own local QuantCoin\texttrademark\,currencies, there would be an enormous monetary incentive to breaking down trade barriers and globalising the network by unifying smaller ones. This is contrary to nationalised fiat currencies, where there is little incentive for, yet much to lose by unifying currencies. Greed on behalf of those owning QuantCoins\texttrademark\,would therefore directly incentivise harmony and integration amongst all the world's leading players in the technological realm. Well-financed market participants would have much to lose from fracturing of the network. This could make QuantCoin\texttrademark\,a major driver towards international peace and prosperity in the quantum world of tomorrow.

>>>>

\dropcap{T}{he} advent of cryptocurrencies\index{Cryptocurrencies} (Sec.~\ref{sec:bitcoin_blockchain}) places the death of fiat currency\index{Fiat currency} firmly on the horizon \latinquote{Deo gratias}. Central banks around the world have been consistently inflating and devaluing national currencies, destroying their integrity through loose print-on-demand monetary policies to finance ever-increasing debt. National currencies and currency unions sit at the brink of crumbling. Can we opt out? Is there an alternative? Let us discuss an alternative!

@@

For these reasons, gold\index{Gold standard} for thousands of years was almost universally accepted as the legally recognised form of tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies like BitCoin\index{Bitcoin} have become widely adopted and even the norm in contemporary hyper-inflating\index{Hyper-inflation} economies like Venezuela where fiat currency has lost all integrity, as the cryptocurrencies exhibit these desired traits, immune to government. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties and constraints that cannot be easily counterfeited.

We propose that units of quantum computation meet these criteria very well. The only way to forge new computations is via investment into infrastructure, which has direct monetary cost and cannot be mitigated. Recent history has shown us that Moore's Law\index{Moore's Law} has made the growth in classical computing power highly predictable and relatively stable over time, and it is to be expected that a quantum Moore's Law\index{Quantum Moore's Law} will hold.

@@

Existing Blockchain-based cryptocurrencies like Bitcoin\index{Blockchain}\index{Bitcoin} (Sec.~\ref{sec:bitcoin_blockchain}) are actually examples of computation-backed currencies, where the mining process requires brute-force computation of a large number of SHA256\index{SHA256} hash functions\index{Hash functions}, to discover hashes satisfying certain constraints. Unfortunately, however, in the case of Bitcoin these computations are perfectly wasted, since they are not solving any problems of merit. Rather miners are made to perform them purely for the sake of imposing artificial scarcity via `proof-of-work'\index{Proof-of-work}\footnote{This proof-of-work notion was originally borrowed from the Hashcash\index{Hashcash} protocol for preventing email spamming.}.

QuantCoin\texttrademark\,\index{QuantCoin\texttrademark} (Sec.~\ref{sec:quant_coin_technical}) on the other hand backs the currency with real-world computations of value, as determined by market participants at the time, a far better utilisation of computational power, with far greater confidence in its objective monetary value. Such a currency is no longer backed purely by the psychology of scarcity\index{Scarcity}, but also the economic value of executing useful quantum algorithms on real-world data. Thanks to homomorphic encryption\index{Homomorphic encryption} and blind quantum computing\index{Blind quantum computation}, users' data may be protected from eavesdropping end-to-end during computation, whilst still allowing the computation to be associated with a unit of cryptocurrency.

@@

Because future contracts have predetermined times until maturity, they also serve the very helpful role of being hedging\index{Hedging} instruments, an important tool for end-users of computation who may wish to lock in prices in advance to mitigate exposure to market risk.

@@

Consider the time-share future contract model\index{Time-sharing} as a basis for a currency. Unlike fiat currency, this monetary system would not be inflationary since the commodity backing the currency is one which cannot be easily counterfeited -- the only way to make more currency is to provide more genuine, functional, online qubits, which increases the money supply over time in tandem with the underlying asset backing it. This would in effect be a full-reserve banking system\index{Full-reserve banking}, where the direct one-to-one convertibility between currency (forward contracts on computation) and its backing asset (time-shared access to physical qubits) eliminates the money multiplier\index{Money multiplier}, a system essentially immune to bank runs\index{Bank runs}.

@@

In a strategically fractured\index{Fracturing} world, where multiple, independent quantum internets may exist in isolation to one another, partitioned along geo-strategic boundaries, each with their own local QuantCoin\texttrademark\,currencies, there would be an enormous monetary incentive to breaking down trade barriers and globalising the network by unifying smaller ones. This is contrary to nationalised fiat currencies, where there is little incentive for, yet much to lose by unifying currencies. Greed on behalf of those owning QuantCoins\texttrademark\,would therefore directly incentivise harmony and integration amongst all the world's leading players in the technological realm. Well-financed market participants would have much to lose from fracturing of the network. This could make QuantCoin\texttrademark\,a major driver towards international peace and prosperity in the quantum world of tomorrow.

### 2018-09-15 Sections/essay_the_economics_of_the_quantum_internet.tex
Proof reading

\dropcap{Q}{uantum} computers are highly likely to, at least initially, be extremely expensive, and affordable outright by few. Client/server economic models based on outsourcing of computations to servers on a network, will be essential to making quantum computing widely accessible. The protocols we have presented here pave the way for this type of economic model to emerge. It is paramount that the types of technologies introduced here be fully developed in time for the deployment of useful quantum computing hardware, such that they can be fully commercialised from day one of their availability, enabling widespread adoption, enhanced economy of scale, and rapid proliferation.

@@

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just last year would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience' (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

The quantum internet will facilitate the communication and trade of quantum assets beyond just quantum computation and cryptography. There are many uses for various hard-to-prepare quantum states, for example in metrology, lithography, or research, where outsourcing complicated state preparation would be valuable. Alternately, performing some quantum measurements can be technologically challenging, and the ability to delegate them to someone better-equipped would be desirable. The quantum internet goes beyond just quantum computing. Rather, it extends to a full range of quantum resources and protocols.\index{State preparation} \index{Measurement}

To commodify quantum computing, if constructing large-scale quantum computers were a simple matter of plug-and-play, where QuantumLego\texttrademark\,building blocks are available off-the-shelf and straightforward to assemble even for monkeys, mass production would rapidly force down prices. By arbitrarily interconnecting these boxes, large-scale quantum computers could be scaled up with demand, with a trajectory following a new Quantum Moore's Law, with potentially super-exponential computational return.

We envisage that each of these commodity items is a black box, within which a relatively small number of qubits are held captive. Then, to build a larger quantum computer, we don't need to upgrade our boxes. Rather, we simply purchase more boxes to interconnect over the network. This notion is tailored to graph states in particular -- because a graph state can be realised by nearest neighbour interactions alone, and since all preparation stages commute with one another, they naturally lend themselves to modularised, distributed preparation.\index{Modularised quantum computation}

@@

By having a standardised architecture for optically interconnecting modules, we also somewhat `future-proof' our hardware investment -- if interfacing modules is standardised, existing hardware can be fully compatible with newer, more capable module versions. We might envision the emergence of open standards on optical interconnects and fusion protocols.

On the other hand, if quantum computers were only ever sold as specialised, room-sized, all-in-one solutions (think D-Wave\texttrademark), such mass production would not experience the driving force of commodified, off-the-shelf building blocks, each of which is cheap, yet frugal in its computational power alone.

Essential to existing financial markets are pricing models for physical assets. Furthermore, derivative markets increase trading liquidity, market efficiency, enhance price discovery, and importantly, allow risk management via hedging and the ability to lock in future prices. This is invaluable to traders of conventional commodities, and it is to be expected that it will be equally valuable to consumers of quantum resources. We have made initial steps in deriving pricing models for quantum assets and derivatives, which although they may require revision in the future real-world quantum marketplace, provide an initial qualitative understanding of quantum market dynamics.

Networked quantum computing will present new challenges for policy-makers, whose fiscal policies strive to maximise economic efficiency and optimise resource allocation. Devising policies of taxation and a regulatory framework in the quantum era will require careful deliberation.

It is evident that taxation of qubits has far deeper economic implications than the taxation of other typical financial assets or classical technologies, owing to their exponential scaling characteristics. Generally speaking, taxation of an asset disincentivises its growth. But if the computational return on quantum assets grows exponentially with network size, so too will sensitivity to taxes that stifle it. This will require extremely prudent consideration when designing fiscal policies in the quantum era, so as to avoid exponential suppression of quantum-related economic activity.

Conversely, the exponential dependence on the rate of taxation could be exploited for leverage via subsidisation. It may be economically beneficial to subsidise quantum infrastructure, reaping its exponential payback, via taxation of other economic sectors, less sensitive to taxation.

>>>>

\dropcap{Q}{uantum} computers are highly likely to, at least initially, be extremely expensive, and affordable outright by few. Client/server economic models based on outsourcing\index{Outsourced quantum computation} of computations to servers on a network, will be essential to making quantum computing widely accessible. The protocols we have presented here pave the way for this type of economic model to emerge. It is paramount that the types of technologies introduced here be fully developed in time for the deployment of useful quantum computing hardware, such that they can be fully commercialised from day one of their availability, enabling widespread adoption, enhanced economy of scale, and rapid proliferation.

@@

Already today, even before the advent of useful post-classical quantum computers, we are seeing the emergence of the outsourced model for computation\index{Outsourced quantum computation}. IBM recently made an elementary 16-qubit quantum computer freely available for use via the cloud. Interested users can log in online, upload a circuit description for a quantum protocol, and have it executed remotely, with the results relayed back in real-time. Although still very primitive, this simple development already makes experimentation with elementary quantum protocols accessible to the poor layman, undergrad, or PhD student in a developing country, people who just a few years ago would never have dreamt of being able to run their own quantum information processing experiments! This effectively opens up research opportunities to people who otherwise would have been priced out of the market entirely, unable to compete with established, well-resourced labs. Evidently, the market already recognises the importance of outsourced models for quantum computation. We encourage the impatiently curious reader to log onto the `IBM Quantum Experience'\index{IBM Quantum Experience} (\href{http://www.research.ibm.com/quantum/}{http://www.research.ibm.com/quantum/}) and take a shot at designing a 16-qubit quantum protocol, without even needing to be in the same country as the quantum computer.

The quantum internet will facilitate the communication and trade of quantum assets\index{Quantum assets} beyond just quantum computation and cryptography. There are many uses for various hard-to-prepare quantum states, for example in metrology, lithography, or research, where outsourcing complicated state preparation would be valuable. Alternately, performing some quantum measurements can be technologically challenging, and the ability to delegate them to someone better-equipped would be desirable. The quantum internet goes beyond just quantum computing. Rather, it extends to a full range of quantum resources and protocols.\index{State preparation}\index{Measurement}

To commodify quantum computing, if constructing large-scale quantum computers were a simple matter of plug-and-play, where QuantumLego\texttrademark\,building blocks\index{QuantumLego\texttrademark} are available off-the-shelf and straightforward to assemble even for monkeys, mass production would rapidly force down prices. By arbitrarily interconnecting these boxes, large-scale quantum computers could be scaled up with demand, with a trajectory following a new Quantum Moore's Law\index{Quantum Moore's Law}, with potentially super-exponential computational return.

We envisage that each of these commodity items is a black box, within which a relatively small number of qubits are held captive. Then, to build a larger quantum computer, we don't need to upgrade our boxes. Rather, we simply purchase more boxes to interconnect over the network -- modularised quantum computation\index{Modularised quantum computation}. This notion is tailored to graph states in particular -- because a graph state can be realised by nearest neighbour interactions alone, and since all preparation stages commute with one another, they naturally lend themselves to modularised, distributed preparation.\index{Modularised quantum computation}

@@

By having a standardised architecture for optically interconnecting modules, we also somewhat `future-proof' our hardware investment -- if interfacing modules is standardised, existing hardware can be fully compatible with newer, more capable module versions. We might envision the emergence of open standards on optical interconnects and fusion protocols\index{Open standards}.

On the other hand, if quantum computers were only ever sold as specialised, room-sized, all-in-one solutions (think D-Wave\texttrademark)\index{D-Wave}, such mass production would not experience the driving force of commodified, off-the-shelf building blocks, each of which is cheap, yet frugal in its computational power alone.

Essential to existing financial markets are pricing models for physical assets. Furthermore, derivative markets increase trading liquidity, market efficiency, enhance price discovery, and importantly, allow risk management via hedging and the ability to lock in future prices\index{Risk management}\index{Hedging}\index{Future contracts}. This is invaluable to traders of conventional commodities, and it is to be expected that it will be equally valuable to consumers of quantum resources. We have made initial steps in deriving pricing models for quantum assets and derivatives, which although they may require revision in the future real-world quantum marketplace, provide an initial qualitative understanding of quantum market dynamics.

Networked quantum computing will present new challenges for policy-makers\index{Policy-making}, whose fiscal policies strive to maximise economic efficiency and optimise resource allocation. Devising policies of taxation and a regulatory framework in the quantum era will require careful deliberation.

It is evident that taxation\index{Taxation} of qubits has far deeper economic implications than the taxation of other typical financial assets or classical technologies, owing to their exponential scaling characteristics. Generally speaking, taxation of an asset disincentivises its growth. But if the computational return on quantum assets grows exponentially with network size, so too will sensitivity to taxes that stifle it. This will require extremely prudent consideration when designing fiscal policies in the quantum era, so as to avoid exponential suppression of quantum-related economic activity.

Conversely, the exponential dependence on the rate of taxation could be exploited for leverage via subsidisation\index{Subsidisation}. It may be economically beneficial to subsidise quantum infrastructure, reaping its exponential payback, via taxation of other economic sectors, less sensitive to taxation.
